Supporting Information

### 2018-02-26 SupportingInformation.Rmd

output: 
  pdf_document:
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
---
updated on `r Sys.Date()`

```{r ,echo=FALSE}
library(captioner)
table_nums <- captioner(prefix = "Table")
fig_nums <- captioner(prefix="Figure")
```

<!--A function needed for caching-->
```{r echo=F}
mtime <- function(files)
{
  lapply(Sys.glob(files),function(x) X =   
          file.info(x)$mtime)
}
```

<!--Setup-->
```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
seed<-101
families<-c(1,3:10,13,14,16:20)
source("getcopula.R")
source("OurBiCopSelect.R")
source("FittingCopula_selective_loc.R")
source("aphid_data_calling.R")
source("plankton_north_sea_data_calling.R")
source("NonParamStat.R")
```

@@

```{r load_data_Loecke, echo=F, fig.cap="plot of the raw data", fig.height=5, fig.width=5}
#Load your data - should be a data frame with 2 columns. Can contain NAs.
d<-readRDS("Data/RaCA_soilorganicC_soiltotalN_stocks100cm.RDS")
d<-d[,c("SOCstock100","TSNstock100")]
fig_nums("soilCNraw",display=F)
plot(d[,1],d[,2],type="p",col="red",xlab="Soil C",ylab="Soil N",cex.lab=1)
rect(0,0,1,1)
```

```{r rankandplot_Loecke, echo=F, fig.cap="Copula plot of soil C/N data",  fig.height=5, fig.width=5}
#convert to a copula and plot
fig_nums("soilCNcop",display=F)
v<-getcopula(d=d,rankon=T,ploton=T) #with real data, rankon should be T
```

@@

# Question 1 analyses for each dataset

Recall that question 1 is: Do datasets in ecology and related fields have non-Gausian copula srtructure? Do they show tail dependence distinct from that of a Gaussian copula? In particular do they show asymmetric tail dependence?

@@

```{r bivmodselect_Loecke, echo=F, cache=T, cache.extra=list(seed,v)}
set.seed(seed)
families_Loecke<-c(1,3:10,13:14,16:20) 
BivMS_res_Loecke<-OurBiCopSelect(u1=v[,1],u2=v[,2],families=families_Loecke,level=0.05,AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,gofnormal=F,status=F)
```

The test of indepedence gave *p=*`r BivMS_res_Loecke$IndepTestRes` . We fitted several copulas
and got AIC values and upper- and lower-tail dependency estimates based on the fitted copulas:

```{r soilCNfit,echo=F}
h<-BivMS_res_Loecke$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
#rownames(h)<-NULL
table_nums("soilCNfit",display=F)
knitr::kable(h, caption = "Fitting info for soilC/N dataset")
```

`r table_nums("soilCNfit",display="c")` shows that several copulas are much better supported than the Gaussian copula, answering the first part of question 1 for these data.

@@

```{r stat_soilCN, echo=F, cache=T, cache.extra=list(seed,v)}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_soilCN/"

stat_soilCN<-copsync(v)
saveRDS(stat_soilCN,paste(resloc,file="stat_soilCN.RDS",sep=''))
sCN<-stat_soilCN[c(2:5,7,8,10:13)]
stat<-unlist(sCN)
```

```{r table_stat_soilCN, echo=F, results="asis"}
table_nums("table_stat_soilCN",display=F)

@@

```{r ,echo=F}
#sCN
CorlmCoru<-stat_soilCN$Corl-stat_soilCN$Coru
cat("Corl-Coru = ",CorlmCoru,"\n")
PlmPu<-stat_soilCN$Pl-stat_soilCN$Pu
cat("Pl-Pu = ",PlmPu,"\n")
TlmTu<-stat_soilCN$Tl-stat_soilCN$Tu
cat("Tl-Tu = ",TlmTu,"\n")
D2umD2l<-stat_soilCN$D2u-stat_soilCN$D2l
cat("D2u-D2l = ",D2umD2l,"\n")
```

<!--Shya could work on this. Select 1-2 statistics, maybe more, but try to cut some of them (looks like there will be 4). Apply to C/N data, get results, display in the same kind of way.-->

>>>>

output: 
  pdf_document:
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
---

updated on `r Sys.Date()`

<!--Shya pls add a short description of what this chunk is for. Should it be in the setup chunk down below?-->
```{r ,echo=FALSE}
library(captioner)
table_nums <- captioner(prefix = "Table")
fig_nums <- captioner(prefix="Figure")
```

<!--Setup-->
```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
seed<-101
families<-c(1,3:10,13,14,16:20)
#A function needed for caching
mtime <- function(files)
{
  lapply(Sys.glob(files),function(x) X =   
          file.info(x)$mtime)
}
source("getcopula.R")
source("OurBiCopSelect.R")
source("FittingCopula_selective_loc.R")
source("aphid_data_calling.R")
source("plankton_north_sea_data_calling.R")
source("NonParamStat.R")
source("copsurrog2d.R")
```

@@

The raw data look like this:
<!--Load the soil C and N data and make a plot-->
```{r load_data_Loecke, echo=F, fig.cap="Plot of the raw soil C and N data.", fig.height=5, fig.width=5}
d<-readRDS("Data/RaCA_soilorganicC_soiltotalN_stocks100cm.RDS")
d<-d[,c("SOCstock100","TSNstock100")]
fig_nums("soilCNraw",display=F)
plot(d[,1],d[,2],type="p",col="red",xlab="Soil C",ylab="Soil N",cex.lab=1)
```

The copula looks like this:
<!--Plot the copula of the soil C and N data--> 
```{r rankandplot_Loecke, echo=F, fig.cap="Copula plot of the soil C and N data",  fig.height=5, fig.width=5}
#convert to a copula and plot
fig_nums("soilCNcop",display=F)
v<-getcopula(d=d,rankon=T,ploton=T) #with real data, rankon should be T
```

@@

# Question 1 analyses for each dataset
Recall that question 1 is: Do datasets in ecology and related fields have non-Gausian copula srtructure? Do they show tail dependence distinct from that of a Gaussian copula? In particular do they show asymmetric tail dependence?

@@

### Model selection approach
```{r bivmodselect_Loecke, echo=F, cache=T, cache.extra=list(seed,v,mtime(list("OurBiCopSelect.R")))}
set.seed(seed)
families_Loecke<-c(1,3:10,13:14,16:20) 
BivMS_res_Loecke<-OurBiCopSelect(u1=v[,1],u2=v[,2],families=families_Loecke,level=0.05,AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,gofnormal=F,status=F)
```
The test of indepedence gave $p=$ `r BivMS_res_Loecke$IndepTestRes`.

We fitted several copulas
and got AIC values and upper- and lower-tail dependency estimates based on the fitted copulas:
```{r soilCNfit,echo=F}
h<-BivMS_res_Loecke$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
table_nums("soilCNfit",display=F)
knitr::kable(h, caption = "Fitting info for soil C and N dataset. Here and henceforth copula names are abbreviated as: N=normal (Gaussian); C=Clayton; G=Gumbel; F=Frank; J=Joe; SC=Survival Clayton; SG=Survival Gumbel; SJ=Survival Joe. An S in front of one of the copulas BB1, BB6, BB7, BB8 indicates the survival version of that copula (rotation by 180 degrees).")
```
`r table_nums("soilCNfit",display="c")` shows that several copulas are much better supported (higher AIC and BIC weights) than the Gaussian copula, answering the first part of question 1 for these data.

@@

<!--DAN: wherever copsync is needs to be sourced and also added to the mlist below-->
```{r stat_soilCN, echo=F, cache=T, cache.extra=list(seed,v,mlist(list("CopulaFunctions.R","copsurrog2d.R")))}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_soilCN/"

#get the stats for the real data
stat_soilCN<-copsync(v) 
saveRDS(stat_soilCN,paste(resloc,file="stat_soilCN.RDS",sep=''))
sCN<-stat_soilCN[c(2:5,7,8,10:13)]
stat<-unlist(sCN)

#get surrogates and get stats for them
cop<-normalCopula(.5,2)
surv<-copsurrog2d(v,cop,1000)
#DAN: once you get the code for copsync, apply it to each surrogate and keep the results
```

<!--DAN: modify the table so it also shows tail asymmetry stats (differences) and also shows fractions of surrogates for both the tail dependence stats and the asymmetry stats that are greater than the real data stat-->
```{r table_stat_soilCN, echo=F, results="asis"}
table_nums("table_stat_soilCN",display=F)

@@

<!--DAN: The below will no longer be necessary once you make the above changes-->
```{r ,echo=F}
#sCN
CorlmCoru<-stat_soilCN$Corl-stat_soilCN$Coru
cat("Corl-Coru = ",CorlmCoru,"\n")
PlmPu<-stat_soilCN$Pl-stat_soilCN$Pu
cat("Pl-Pu = ",PlmPu,"\n")
TlmTu<-stat_soilCN$Tl-stat_soilCN$Tu
cat("Tl-Tu = ",TlmTu,"\n")
D2umD2l<-stat_soilCN$D2u-stat_soilCN$D2l
cat("D2u-D2l = ",D2umD2l,"\n")
```
